The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-05 src/ms.tex
Fix a handful of typos

% Much of this text was adapted from Robel Geda's report from NSBP and
% SACNAS. Please include him on the author list.
\textbf{\astropy representation at national diversity conferences:}
Several members of the \astropy community attended virtual conferences of the
National Society of Black Physicists (NSBP) and SACNAS (focusing on Hispanic and
Native American scientists across all STEM fields). \astropy representatives
noted that one underlying topic came up multiple times. A major barrier for
persons who come from underrepresented communities is the lack of resources and
expertise that are necessary to train students. Writing PEP 8-compliant software
and understanding the Git and \github workflow is not part of the standard
Physics and Astrophysics curriculum. Additionally, the larger astronomical
community is still in the process of transitioning towards \python-based tools,
making it difficult for students not currently under advisement by some one with
extensive \python expertise to get involved with the open-source \python
community. Projects such as Learn Astropy (see Section~\ref{sec:learn}) could
have a profound impact by empowering underrepresented groups because it provides
a free, searchable, and accessible introduction to \python tools for
astrophysical research. Representatives also noted that offering training and
teaching materials to PIs of Research Experience for Undergraduate (REU)
programs throughout the United States could be helpful for encouraging advisors
to teach students how to use Astropy, create their own libraries, and use
version control on open-source platforms like \github. Such materials could also
be offered as a workshop at national diversity conferences themselves, as SACNAS
solicits special session proposals each year.

@@

Sphinx is a common and useful tool for generating documentation for Python
packages. The Astropy project maintains a default Sphinx configuration along
with Astropy-specific extensions that can be easily added to community
projects via the
\href{https://github.com/astropy/sphinx-astropy}{\texttt{sphinx-astropy}} meta
package. This tool provides a pre-configured Sphinx setup compatible with
Astropy projects, which includes several extensions useful for generating API
documentation
(\href{https://github.com/astropy/sphinx-automodapi}{\texttt{sphinx-automodapi}}),
allowing for \package{numpy} docstring parsing
(\href{https://github.com/numpy/numpydoc}{\texttt{numpydoc}}), embedded image
handling
(\href{https://github.com/sphinx-gallery/sphinx-gallery}{\texttt{sphinx-gallery}};
\href{https://github.com/python-pillow}{\texttt{pillow}}), advanced
documentation testing support
(\href{https://github.com/astropy/pytest-doctestplus}{\texttt{pytest-doctestplus}}),
and providing a custom documentation theme ideal for analysis packages
(\href{https://github.com/astropy/sphinx-astropy}{\texttt{astropy-sphinx-theme}}).

@@

Likewise, JWST developers have provided significant contributions
to the \package{photutils} \citep{photutils}, \package{specutils}
\citep{specutils}, and \package{regions} \citep{regions} coordinated
packages and the \package{gwcs} \citep{gwcs} and \package{synphot}
\citep{synphot} affiliated packages. For example, development of the
\package{photutils} coordinated package for source detection and
photometry has largely been led by JWST contributions. JWST developers
have also made significant contributions to the \package{specutils}
coordinated package, which is used for analyzing spectroscopic data,
and the \package{regions} coordinated package, which is used to
handle geometric regions. The \package{gwcs} affiliated package for
generalized world coordinate systems was created specifically to handle
the complex world coordinate systems needed for JWST spectroscopic
data. The \package{synphot} affiliated package for synthetic photometry
was created at STScI and is a dependency of the JWST exposure-time
calculators. Further, the \package{ASDF} (Advanced Scientific Data
Format) package \citep{ASDF}, a next-generation interchange format for
scientific data, was initially developed at STScI to serialize JWST WCS
objects along with \astropypkg models, units, and coordinates. Over
its mission lifetime, JWST will continue its support in developing and
maintaining these critically dependent packages.

@@

  This kind of communication may provide bias pespectives on these communities.

>>>>

% Much of this text was adapted from Robel Geda's report from NSBP and
% SACNAS. Please include him on the author list.
\textbf{\astropy representation at national diversity conferences:}
Several members of the \astropy community attended virtual conferences of the
National Society of Black Physicists (NSBP) and SACNAS (focusing on Hispanic and
Native American scientists across all STEM fields). \astropy representatives
noted that one underlying topic came up multiple times. A major barrier for
persons who come from underrepresented communities is the lack of resources and
expertise that are necessary to train students. Writing PEP 8-compliant software
and understanding the Git and \github workflow is not part of the standard
Physics and Astrophysics curriculum. Additionally, the larger astronomical
community is still in the process of transitioning towards \python-based tools,
making it difficult for students not currently under advisement by someone with
extensive \python expertise to get involved with the open-source \python
community. Projects such as Learn Astropy (see Section~\ref{sec:learn}) could
have a profound impact by empowering underrepresented groups because it provides
a free, searchable, and accessible introduction to \python tools for
astrophysical research. Representatives also noted that offering training and
teaching materials to PIs of Research Experience for Undergraduate (REU)
programs throughout the United States could be helpful for encouraging advisors
to teach students how to use Astropy, create their own libraries, and use
version control on open-source platforms like \github. Such materials could also
be offered as a workshop at national diversity conferences themselves, as SACNAS
solicits special session proposals each year.

@@

Sphinx is a common and useful tool for generating documentation for Python
packages. The Astropy project maintains a default Sphinx configuration along
with Astropy-specific extensions that can be easily added to community
projects via the
\href{https://github.com/astropy/sphinx-astropy}{\texttt{sphinx-astropy}}
meta-package. This tool provides a pre-configured Sphinx setup compatible with
Astropy projects, which includes several extensions useful for generating API
documentation
(\href{https://github.com/astropy/sphinx-automodapi}{\texttt{sphinx-automodapi}}),
allowing for \package{numpy} docstring parsing
(\href{https://github.com/numpy/numpydoc}{\texttt{numpydoc}}), embedded image
handling
(\href{https://github.com/sphinx-gallery/sphinx-gallery}{\texttt{sphinx-gallery}};
\href{https://github.com/python-pillow}{\texttt{pillow}}), advanced
documentation testing support
(\href{https://github.com/astropy/pytest-doctestplus}{\texttt{pytest-doctestplus}}),
and providing a custom documentation theme ideal for analysis packages
(\href{https://github.com/astropy/sphinx-astropy}{\texttt{astropy-sphinx-theme}}).

@@

Likewise, JWST developers have provided significant contributions
to the \package{photutils} \citep{photutils}, \package{specutils}
\citep{specutils}, and \package{regions} \citep{regions} coordinated
packages and the \package{gwcs} \citep{gwcs} and \package{synphot}
\citep{synphot} affiliated packages. For example, development of the
\package{photutils} coordinated package for source detection and
photometry has largely been led by JWST contributions. JWST developers
have also made significant contributions to the \package{specutils}
coordinated package, which is used for analyzing spectroscopic data,
and the \package{regions} coordinated package, which is used to
handle geometric regions. The \package{gwcs} affiliated package for
generalized world coordinate systems was created specifically to handle
the complex world coordinate systems needed for JWST spectroscopic
data. The \package{synphot} affiliated package for synthetic photometry
was created at STScI and is a dependency of the JWST exposure-time
calculators. Furthermore, the \package{ASDF} (Advanced Scientific Data
Format) package \citep{ASDF}, a next-generation interchange format for
scientific data, was initially developed at STScI to serialize JWST WCS
objects along with \astropypkg models, units, and coordinates. Over
its mission lifetime, JWST will continue its support in developing and
maintaining these critically dependent packages.

@@

  This kind of communication may provide biased perspectives on these
